---
title: "Visualizations and Interactive Graphics using R"
---


✏️ Haley Jeppson, Brian Habing\
🗓 April 12, 2023\
⏰ 1:00 PM - 5:00 PM CDT\

<br/><br/>

### Schedule


| Activity |
|:------------------------------------|
| Session 1: [Introduction to ggplot2](materials/introduction.html)|
| Session 2: [ggplot2 concepts](materials/ggplot-concepts.html) |
| Session 3: [Advanced Customization](materials/advanced-customization.html)|
| Session 4: [Extensions & Interactivy](materials/extensions.html)| 


<br/><br/>

## Prerequisites

We will be working with the most recent stable versions of R and RStudio, as well as with a number of additional packages.

### Install R and RStudio

You will need:

R version >= 4.1
RStudio >= 2022.02.1

### Review

This [ebook](https://haleyjeppson.github.io/R4QM/an-introduction.html) provides an introduction to R programming and serves as a companion to the data visualization workshop at NCME.




### Install the necessary CRAN packages

```{r eval = FALSE}
my_packages <- c("rmarkdown", "knitr", "tidyverse",
                 'patchwork', "cowplot",  'colorspace', 
                 'ggtext', 'ggokabeito', 'ggthemes',
                 'ggdist', 'GGally', 'ggrepel', 
                 'ggpubr', 'ggstatsplot', 'ggdag', 
                 'plotly', 'ggiraph')

install.packages(my_packages)
```



### Install R package development toolchain {#install-r-package-development-toolchain}

(installation notes from [Ian Lyttle](https://github.com/ijlyttle))

#### For Windows with no admin rights

Download the latest (recommended) Rtools installer, `Rtools.exe`, from <https://cran.r-project.org/bin/windows/Rtools/>. Run the installer keeping the default settings.

#### For Windows with admin rights

Download the latest (recommended) Rtools installer, `Rtools.exe`, from <https://cran.r-project.org/bin/windows/Rtools/>. Run the installer making the following selections: keep the default settings for the installation location and components to install; check the box to add rtools to the system PATH.

#### For Mac

Install XCode. Either:

1.  Download and install XCode from the Mac AppStore: <http://itunes.apple.com/us/app/xcode/id497799835?mt=12>
2.  Within XCode go to Preferences : Downloads and install the Command Line Tools

Or for a smaller download size:

1.  Register as an Apple Developer (free) here: <https://developer.apple.com/programs/register/>
2.  Download the Command Line Tools for XCode appropriate for the version of OS X you are running from here: <https://developer.apple.com/downloads/>

#### For Linux

If you installed `r-base-dev`, when installing R, you should have all you need to build packages from source. Otherwise return to the instructions for installing R for your distribution and follow the instructions there to install the additional tools.






### Install the **`devtools`** and **`NCME23data`** packages {#packages}

The aim of **`devtools`** is to make package development easier by providing R functions that simplify and expedite common tasks. The [R Packages](https://r-pkgs.org/) book and the Building Tidy Tools workshop are based on a **`devtools`** workflow.

Install **`devtools`**:

```{r eval = FALSE}
install.packages("devtools")
```

After installing the [R package development toolchain](#install-r-package-development-toolchain) and **`devtools`**, you can verify your system is set up by running:

```{r eval = FALSE}
devtools::has_devel()
```


Install **`NCME23data`** from GitHub:

```{r eval = FALSE}
devtools::install_github("haleyjeppson/NCME23data")
```


Install **`ggcorrplot`** from GitHub:

```{r eval = FALSE}
devtools::install_github("kassambara/ggcorrplot")
```


